---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fletcher

The goal of fletcher is to convert [quiver notebooks](http://happenapps.com/#quiver) to markdown documents.

## Installation

You can install the released version of fletcher from [CRAN](https://CRAN.R-project.org) with:

``` r
remotes::install_github("dpastoor/fletcher")
```

## motivation

Quiver is a fantastic tool for documenting, however there are some limitations, such
as being mac only and rendering only within the quiver app. In many cases, 
creating documentation makes sense within quiver, taking advantages of its functionality to 
easily embed images via copy/paste, code cells for organization, search
functionality, etc. Once docs need to be pushed to git, or other knowledge bases, 
a more standard format might be needed. This tool allows the seemless translation
between the quiver cells (code/markdown) to markdown documents.


```{r}
devtools::session_info()
```

